\documentclass{beamer}

% Preamble
\usepackage[utf8]{inputenc}
\usepackage{graphicx} 
\usepackage{amsmath} 
\usepackage{hyperref} 
\usepackage{xcolor} 

% Theme setup
\usetheme{Madrid} 
\usecolortheme{dolphin}

% Title page details
\title{Age from brain Data}
\subtitle{Project presentation}
\author{Marco Accerenzi}
\institute{Università di Pisa - Dipartimento di Fisica}
\date{\today}

% Begin the document
\begin{document}

% Title Slide
\begin{frame}
    \titlepage
\end{frame}

% Table of Contents
\begin{frame}{Outline}
    \tableofcontents
\end{frame}

% First Slide
\section{Introduction}
\begin{frame}{Introduction to the Topic}
    \begin{itemize}
        \item Regression model.
        \item What's Keras.
        \item Training.
    \end{itemize}
\end{frame}

% Second Slide with Equations
\section{Data manipulations}
\begin{frame}{Data manipulations}
    \begin{itemize}
        \item Pandas.
        \item Extracting arrays and Numpy.
        \item Normalising the data.
    \end{itemize}
\end{frame}

% Third Slide with an Image
\section{Training the model}
\begin{frame}{Including an Image}
	\begin{itemize}
		\item Learning algorithms.
		\item loss function and optimization.
		\item Callbacks:
		\begin{itemize}
			\item EarlyStopping and patience.
			\item Reducing the learning rate.
		\end{itemize}
    \end{itemize}
\end{frame}

% Fourth Slide
\section{Optimizing the model's parameters}
\begin{frame}{Optimizing the model's parameters}
	\begin{itemize}
		\item Layers and nodes.
		\item Validation split.
		\item Shuffling the data.
	\end{itemize}
\end{frame}

% Fifth slide
\section{Training history}
\begin{frame}{Including an Image}
    \begin{itemize}
        \item Learning algorithms.
        \item loss function and optimization.
        \item Callbacks:
	\begin{itemize}
		\item EarlyStopping and patience
		\item Reducing the learning rate
	\end{itemize}
    \end{itemize}
\end{frame}

% Closing slide
\section{Results and conclusion}
\begin{frame}{Results and conclusion}
    \begin{itemize}
		\item Final values for the loss function and mean error.
		\item Evaluating new data.
    \end{itemize}
\end{frame}

% Backup slides
\section*{Making an interface for the user}
\begin{frame}{Making an interface for the user}
    \begin{itemize}
		\item to do
    \end{itemize}
\end{frame}

\end{document}
